FocalGstar

### 2017-06-17 analysis.Rmd
updated code to generate quantile-based hotspots

```{r demo-zoom-gstar, echo=FALSE, cache=TRUE, fig.width=7, fig.height=4.5}
z <- 0
for (g in zoom_gstar) {
  z <- z + 1
  plot_zscore(g,
              title = sprintf("Standard G*: zoom=%d", z),
              sigma_thresh = 2)
}
```

@@

```{r demo-zoom-focalgstar, echo=FALSE, cache=TRUE, fig.width=6, fig.height=5.5}
z <- 0
for (g in zoom_focalgstar) {
  z <- z + 1
  plot_zscore(g,
              title = sprintf("Focal G*: zoom=%d", z),
              sigma_thresh = 2)
}
```

@@

```{r demo-blur-gstar, echo=FALSE, cache=TRUE, fig.width=6, fig.height=5.5}
for (i in seq_along(wsizes)) {
  ws <- wsizes[i]
  g <- blur_gstar[[i]]
  plot_zscore(g,
              title = sprintf("Standard G*: wsize=%d", ws),
              sigma_thresh = 2)
}
```

@@

```{r demo-blur-focalgstar, echo=FALSE, cache=TRUE, fig.width=6, fig.height=5.5}
for (i in seq_along(wsizes)) {
  ws <- wsizes[i]
  g <- blur_focalgstar[[i]]
  plot_zscore(g,
              title = sprintf("Focal G*: wsize=%d", ws),
              sigma_thresh = 2)
}
```

>>>>

```{r demo-zoom-gstar, echo=FALSE, cache=TRUE, fig.width=4, fig.height=4}
for (g in zoom_gstar) {
  plot_zscore(g, sigma_thresh = 2, show.legend = FALSE)
}
```

@@

```{r demo-zoom-focalgstar, echo=FALSE, cache=TRUE, fig.width=4, fig.height=4}
for (g in zoom_focalgstar) {
  plot_zscore(g, sigma_thresh = 2, show.legend = FALSE)
}
```

@@

```{r demo-blur-gstar, echo=FALSE, cache=TRUE, fig.width=4, fig.height=4}
for (g in blur_gstar[RENDERED_IDX]) {
  plot_zscore(g, sigma_thresh = 2, show.legend = FALSE)
}
```

@@

```{r demo-blur-focalgstar, echo=FALSE, cache=TRUE, fig.width=6, fig.height=5.5}
for (g in blur_focalgstar[RENDERED_IDX]) {
  plot_zscore(g, sigma_thresh = 2, show.legend = FALSE)
}
```
